Untitled

### 2025-03-03 code/manuscript_altanalysis.Rmd
final changes

  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year ,
        #first_stage = ~ TotalPop + PctMedicaid + PctUninsured + PctPoverty + PctBlack + PctHispanic + PctChildren + PctElderly | ID + Year ,
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

>>>>

  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        #first_stage = ~ 1 | ID + Year ,
        first_stage = ~ TotalPop + PctMedicaid + PctUninsured + PctPoverty + PctBlack + PctHispanic + PctChildren + PctElderly | ID + Year ,
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )
